### 2017-08-19 paper/incomeShocks-jde-r1.tex
Add community level clustering results to Appendix

We begin by estimating OLS and community and individual level fixed effects 
versions of the following equation:
\begin{align}
Y_{i,t} &=  \beta_1 S_{i,t}  +\boldsymbol{D_{i}}'\boldsymbol{\alpha} 
+ \mu_i + \varepsilon_{i,t},   \label{eq:fixed_effects} 
\end{align}
where $Y_{i,t}$ is the outcome of interest,  
$S_{i,t}$ is whether the household experienced a shock in the relevant period,
$\boldsymbol{D_{i}}$ is a vector of survey wave dummies, 
and $\mu_i$ is time-invariant individual specific characteristics.
With the outcomes of interest all dichotomous, the estimated equations 
are linear probability models. 
For the outcome variables, currently pregnant and contraceptive use, we use 
the dummy variable for crop loss that occurred in the period immediately 
prior to the interview, which is 6 to 7 months long, as our main explanatory 
variable of interest. 
When we use birth as the outcome variable, 
we use the dummy variable for crop loss that occurred in the period between 
the prior two survey rounds.%
\footnote{
In the tables we indicate this difference by referring to the period 
immediately before the survey as 1-7 months and the period between the
prior survey and the survey before that as 7-14 months.
}

To further investigate whether the response to shock vary by household
characteristics, we also estimate individual level fixed effects versions 
of the following equation:
\begin{align}
Y_{i,t} &=  \beta_1 S_{i,t}  +  \beta_2 S_{i,t} \times X_{i,1} +
\boldsymbol{D_{i}}'\boldsymbol{\alpha} + \mu_i + \varepsilon_{i,t},   
\label{eq:fixed_effects} 
\end{align}
where $X_{i,1}$ are either assets holdings at the time of the first
survey or education levels of the respondent or household head.

@@

% OLS estimates

% Pregnancy and birth results
\input{../tables/appendix_pregnant_birth.tex}

% Contraceptives results
\input{../tables/appendix_contraceptives.tex}

% Community level clustering for two main tables

\begin{table}[htbp]
\begin{center}
\begin{threeparttable}
\caption{The Effects of Crop Loss on Pregnancy and Births}
\label{tab:com_cluster_birth}
\begin{tabular}{@{} l D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5}  @{}}
\toprule
                                                       &\multicolumn{3}{c}{Currently pregnant}&\multicolumn{3}{c}{Birth since last survey}\\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
                                                       &                     & \mct{Fixed Effects}                       &                     & \mct{Fixed Effects}                       \\ \cmidrule(lr){3-4} \cmidrule(lr){6-7}
                                                       & \mco{OLS}           & \mco{Community}     & \mco{Woman}         & \mco{OLS}           & \mco{Community}     & \mco{Woman}         \\ \midrule
Crop loss - 1-7 months                                 &      -0.053         &      -0.074         &      -0.093\sym{*}  &                     &                     &                     \\
\hs (200 TZS or above)                                 &     (0.041)         &     (0.045)         &     (0.049)         &                     &                     &                     \\
Crop loss - 7-14 months                                &                     &                     &                     &      -0.103\sym{***}&      -0.115\sym{***}&      -0.159\sym{***}\\
\hs (200 TZS or above)                                 &                     &                     &                     &     (0.036)         &     (0.039)         &     (0.046)         \\
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Community fixed effects                                &    \mco{No}         &    \mco{Yes}        &    \mco{No}         &    \mco{No}         &    \mco{Yes}        &    \mco{No}         \\
Woman fixed effects                                    &    \mco{No}         &    \mco{No}         &    \mco{Yes}        &    \mco{No}         &    \mco{No}         &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{741}        &    \mco{741}        &    \mco{741}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule    
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
All models are linear probability models.
Robust standard errors clustered at community level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
% Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[htbp]
\begin{center}
\begin{threeparttable}
\caption{The Effects of Crop Loss on Contraceptive\\ Use Overall and By Type}
\label{tab:com_cluster_contraceptive}
\begin{tabular}{@{} l D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
\toprule
                                                       &                     & \mct{Fixed Effects}                       \\ \cmidrule(lr){3-4} 
                                                       & \mco{OLS}           & \mco{Community}     & \mco{Woman}         \\ \midrule
                                                       &\multicolumn{3}{c}{Any contraception}  \\ \cmidrule(lr){2-4}
Crop loss - 1-7 months (200 TZS or above)              &       0.061\sym{***}&       0.059\sym{**} &       0.070\sym{**} \\
                                                       &     (0.022)         &     (0.024)         &     (0.032)         \\
\addlinespace 
                                                       &\multicolumn{3}{c}{Traditional contraception}  \\ \cmidrule(lr){2-4}
Crop loss - 1-7 months (200 TZS or above)              &       0.052\sym{**} &       0.048\sym{**} &       0.054\sym{**} \\
                                                       &     (0.021)         &     (0.022)         &     (0.025)         \\
\addlinespace 
                                                       &\multicolumn{3}{c}{Modern contraception}  \\ \cmidrule(lr){2-4}
Crop loss - 1-7 months (200 TZS or above)              &      -0.001         &       0.004         &       0.003         \\
                                                       &     (0.013)         &     (0.013)         &     (0.021)         \\
\addlinespace                                                        
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Community fixed effects                                &    \mco{No}         &    \mco{Yes}        &    \mco{No}         \\
Woman fixed effects                                    &    \mco{No}         &    \mco{No}         &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
All models are linear probability models.
Robust standard errors clustered at community level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
% Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

>>>>

We begin by estimating OLS and community and individual level fixed effects 
versions of the following equation:
\begin{align}
Y_{i,t} &=  \beta_1 S_{i,t}  +\boldsymbol{D_{i}}'\boldsymbol{\alpha} 
+ \mu_i + \varepsilon_{i,t},   \label{eq:fixed_effects1} 
\end{align}
where $Y_{i,t}$ is the outcome of interest,  
$S_{i,t}$ is whether the household experienced a shock in the relevant period,
$\boldsymbol{D_{i}}$ is a vector of survey wave dummies, 
and $\mu_i$ is time-invariant individual specific characteristics.
With the outcomes of interest all dichotomous, the estimated equations 
are linear probability models. 
For the outcome variables, currently pregnant and contraceptive use, we use 
the dummy variable for crop loss that occurred in the period immediately 
prior to the interview, which is 6 to 7 months long, as our main explanatory 
variable of interest. 
When we use birth as the outcome variable, 
we use the dummy variable for crop loss that occurred in the period between 
the prior two survey rounds.%
\footnote{
In the tables we indicate this difference by referring to the period 
immediately before the survey as 1-7 months and the period between the
prior survey and the survey before that as 7-14 months.
}

To further investigate whether the response to shock vary by household
characteristics, we also estimate individual level fixed effects versions 
of the following equation:
\begin{align}
Y_{i,t} &=  \beta_1 S_{i,t}  +  \beta_2 S_{i,t} \times X_{i,1} +
\boldsymbol{D_{i}}'\boldsymbol{\alpha} + \mu_i + \varepsilon_{i,t},   
\label{eq:fixed_effects2} 
\end{align}
where $X_{i,1}$ are either assets holdings at the time of the first
survey or education levels of the respondent or household head.

@@

% Full OLS and community fixed effects results for Pregnancy and birth
\input{../tables/appendix_pregnant_birth.tex}

% Community clustering for pregnancy and birth results
\input{../tables/appendix_cluster_pregnant_birth.tex}

% Full OLS and community fixed effects results for Contraceptives results
\input{../tables/appendix_contraceptives.tex}

% Community clustering for for contraceptives results
\input{../tables/appendix_cluster_contraceptives.tex}
